TODO: A Survey of StarCraft AI Techniques

### 2012-05-04 survey.tex

Thanks to the recent organization of international game AI competitions focused around the popular StarCraft game (see Section \ref{sec:competition}), several groups have been working on integrating many of the techniques described in the previous section into complete ``bots'', capable of playing complete StarCraft games. In this section we will overview some of the currently available top bots, and focus on the architecture being used to integrate all the techniques being used for the different aspects of the bot.

@@

On the other hand, bots such as NOVA or BroodwarBotQ (BBQ) only use a hierarchical organization for {\em micro-management} (controlling the attack units), but use a decentralized organization for the rest of the bot. In Nova and BBQ, there is a collection of modules that control different aspects of the game (workers, production, construction, etc.). These modules can all send actions directly to Starcraft. In Nova those modules coordinate only through writing data in a shared blackboard, and in BBQ they coordinate only when they have to use a shared resource (unit) by means of an arbitrator.

@@

In conclusion, we can see that there are two basic tools that can be used in an integration architecture: abstraction and divide-and-conquer, which are widely used by the existing Starcraft bots. However, several open questions remain:

{\color{red}
This section is missing:
\begin{itemize}
\item Strengths and weaknesses?
\item Which AI techniques do each bot use for each task?
\end{itemize}
}

>>>>

Thanks to the recent organization of international game AI competitions focused around the popular StarCraft game (see Section \ref{sec:competition}), several groups have been working on integrating many of the techniques described in the previous section into complete ``bots'', capable of playing complete StarCraft games. In this section we will overview some of the currently available top bots, and focus, first on the architecture being used to integrate all the techniques being used for the different aspects of the bot, and then on which subsets of techniques are used for each bot.

\subsection{RTS Bot Architectures}\label{sec:integration}

@@

On the other hand, bots such as NOVA or BroodwarBotQ (BBQ) only use a hierarchical organization for {\em micro-management} (controlling the attack units), but use a decentralized organization for the rest of the bot. In Nova and BBQ, there is a collection of modules that control different aspects of the game (workers, production, construction, etc.). These modules can all send actions directly to Starcraft. In Nova those modules coordinate mostly through writing data in a shared blackboard, and in BBQ they coordinate only when they have to use a shared resource (unit) by means of an arbitrator.

@@

In conclusion, we can see that there are two basic tools that can be used in an integration architecture: abstraction and divide-and-conquer, which are widely used by the existing Starcraft bots.

This section has focused on discussing the architecture of existing Starcraft bots. Let us now focus on what is the state of the art on the techniques used for each of the individual modules used by them.

\subsection{Individual AI Techniques}\label{sec:techniques}

{\color{red} TODO}
